\bf\mftitle

### 2011-03-02 doc/jInfer/paper/paper.tex
progres

\documentclass[a4paper,10pt,oneside,twocolumn]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
%\usepackage[scale=0.9]{tgcursor}
%\usepackage[scale=0.9]{tgheros}
\usepackage{xstring}
\usepackage{wrapfig}

@@

\section*{Short architecture overview}
We divide the process of inference into three steps:
\begin{enumerate}
	\item 
	TODO steps, graph from architecture, short mention of internal structure = grammar
\end{enumerate}	
\section*{Extensibility}
TODO short description of how easily can framework be extended ??? maybe not

>>>>

\documentclass[a4paper,8pt,oneside,twocolumn]{article}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
%\usepackage[scale=0.9]{tgcursor}
%\usepackage[scale=0.9]{tgheros}
\usepackage{xstring}
\usepackage{wrapfig}

@@

\section*{Short architecture overview}
\begin{figure}
	\centering\includegraphics[width=\myscale\columnwidth]{inference_process}
	\caption{High-level view of the inference process} \label{inference_process}
\end{figure}
We divide the inference process into three steps (as illustrated on fig. \ref{inference_process}):
\begin{enumerate}
	\item Import of various formats (XML/XSD/DTD/XPath) into internal representation - \emph{Initial Grammar}.
	\item Simlification (generalization) of \emph{Initial Grammar} with optional help of user interaction.
	\item Export into various schema formats (XSD/DTD).
\end{enumerate}	
Our internal representation consist of regular grammar, that is list of rules.
We represent right side of grammar rule as regular expression with our own set of classes to represent regular expressions.

On input, all various formats are first converted into internal representation - from XML rules are extracted as positive examples, concatenations, from XSD/DTD rules are extracted as ther are written in schemata. From XPath we extract only explicit concatenations for now.

Rules are send to \jmodule{Simplifier} module, which has to do the simplification algorithm and return \emph{Simplified Grammar}, which is then easily exporter by exporter modules.

Simplification can be either automatic, or user-aided.
We provide visualization of non-deterministic finite automatons.
This helps algorithms that use merging state algorithm with user interaction.
Using simple API, algorithm developer can call our library to present automaton to user to make human decisions and continue in simplification process.

We provide visualization of rules itself, which is useful for methods not using automatons at all.
Algorithm can use API to display rules

\section*{Extensibility}
Developers willing to experiment with their own algorithms have to take care only of \jmodule{Simplifier} module.
We provide sample one, which is divided into submodules again, and again and again.
One can find exact place he wants to replace functionality, and replace only that part of simplification chain.
It then remains configurable whether to use his new experimental module or the old one, from GUI.
He doesn't need to code into jInfer sources, keeping his software installed in same NB instance as jInfer is enough.
